---
title: "US Vehicle MPG Data"
author: "Biqing Sheng"
date: "2/18/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny App

- The shiny application: https://pipposheng.shinyapps.io/DDPmpg/

- The source code on Github: https://github.com/pipposheng/DDPfinalproject


## Introduction to Analysis

- The purpose of this study is to evaluate the fuel efficiency (MPG) of vehicles with different parameters.
- The paramters considered in this study are: hp (horsepower), cyl(number of cylinder), gear (number of gear), and am (manual or auto transmission).
- The prediction of MPG is based on hp for different cyl, gear, and am.

## MPG Scatterplot

```{r plot, message=FALSE, warning=FALSE}
library(plotly)
plot_ly(data = mtcars, x= ~hp, y = ~cyl, z = ~mpg, type = "scatter3d", color = ~factor(am))
```

## Conclusions

- The user can select cylinder, Gear, and Transmission to get different output plots between mpg and hp.
- The user can predict the fuel efficiency from the hp of the vehicle.
- Due to the limited sample size, some plots are not shown correctly, and some predictions are not available.
